Euler's polyhedron formula

### 2016-02-10 mandatory_assignment/main.tex
meeting notes

\begin{abstract}
   In this short paper we look at Euler's polyhedron formula. This formula was
   one of my first experiences with more abstract mathematics, and I have loved
   it ever since. The proof is very simple, and extremely elegant.
\end{abstract}
\maketitle

@@

We now have two possible transformations to iterate: 
\begin{enumerate}
    \item Remove a triangle with one edge adjacent to the exterior as shown in
        the middle image in figure \ref{fig:proof}.  
    \item Remove a triangle
        with two edges adjacent to the exterior as shown in the rightmost image
        in figure \ref{fig:proof}.
\end{enumerate}
Note that neither of these operations change the quantity of interest. One
removes one edge and one face and the other removes one vertex, two edges, and
one face. We apply these transformations while always keeping the requirement
that the outer edges form a simple cycle. We will eventually end up with a
triangle with three vertices, three edges and one face.

\end{document}

>>>>

\begin{abstract}
   In this short paper we look at Euler's polyhedron formula. This formula was
   one of my first experiences with more abstract mathematics, and I have loved
   it ever since. The proof we consider here is very simple, however there is a
   surprising amount of different proofs for this same result. \cite{proofs}
   presents a list of 20 of them.
\end{abstract}
\maketitle

@@

We now have two possible transformations to iterate: 
\begin{enumerate}
    \item Remove a triangle with one edge adjacent to the exterior as shown in
        the middle image in figure \ref{fig:proof}.  
    \item Remove a triangle
        with two edges adjacent to the exterior as shown in the rightmost image
        in figure \ref{fig:proof}.
\end{enumerate}
Note that neither of these operations change the quantity of interest. One
removes one edge and one face and the other removes one vertex, two edges, and
one face. We apply these transformations while always keeping the requirement
that the outer edges form a simple cycle. We will eventually end up with a
triangle with three vertices, three edges and one face. This final shape
clearly satisfies ${V - E + F = 1}$.  Adding the face we removed when producing
the Schlegel-diagram gives us ${V - E + F = 2}$.

\begin{thebibliography}{9}
    \bibitem{proofs}
        http://www.ics.uci.edu/~eppstein/junkyard/euler/all.html
\end{thebibliography}
\end{document}
